---
title       : Developing Data Products Shiny
subtitle    : Regression Through Origin
author      : Coursera Data Science Project
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## 1. Developing Data Products

We will develop a Data Product using Shiny R package.
Shiny makes it easy to build interactive web applications with R. 

--- .class #id 

## 2. Data Source

We compare children's height and their parents heights using Galtons data from 'UsingR' package.

You will get to find a Line that minimizes the mean squared error (mes) in predicting if parents height have effect on child's height.

---

## 3. Data

Hear is head of data used. We are interested in child and parent height.
```{r }
library(UsingR)
data(galton)
summary(galton)
```

---
  

## 4. Code

Code for this presentation is available on [Github Repository](https://github.com/oromia/DevDataProd)

---

## 5. MSE Calculation

code used to calculate MSE and draw plot
beta is user's input (here we set it to .82)
```{r, echo=FALSE, fig.height=4}
beta <- 0.82
data(galton)
y <- galton$child - mean(galton$child)
x <- galton$parent - mean(galton$parent)

freqData <- as.data.frame(table(x,y))
names(freqData) <- c("child", "parent", "freq")

plot(    as.numeric(as.vector(freqData$parent))
         , as.numeric(as.vector(freqData$child))
         , pch = 21
         , col = "black"
         , bg = "yellow"
         , cex = .15 * freqData$freq 
         , xlab = "Parents"
         , ylab = "Chlidren"
)
abline(0, beta,lwd = 3, col="blue")
points(0,0, cex = 2, pch = 19, col="red")
mse <- mean( (y - beta * x)^2  )
ttl <- paste( "mse = ", round(mse,3), "  ")
title( ttl, col="red")
```
